\documentclass[a4paper,11pt]{article}  % for A4 size paper, standart font size 11 or 12 pt
\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry} % for setting margins, standart 1in, if needed 0.5in
\usepackage{enumitem}  % for customizing lists
\usepackage{amsmath} % for math
\usepackage{setspace} % for line spacing
\usepackage{titlesec} % for customizing section titles
\usepackage{array}   % for defining column width in tables
\usepackage{multicol} % for multiple columns
\usepackage{comment}  % for multi-line comments
\usepackage{ragged2e} % for text alignment, such as justifying




\titleformat{\section}{\normalfont\Large\bfseries}{}{0em}{}[\titlerule] % for section titles

\begin{document}

\begin{center}
    {\fontsize{18pt}{22pt}\selectfont \textbf{Krit Nicol}} \\
    \vspace{0.2in}
    +41-78-632-77-49 \, \textbullet \, krit@nicolkrit.ch \, \textbullet \, linkedin.com/in/krit-pio-nicol \, \textbullet \, Agno, Ticino \\
\end{center}

\vspace{0.2in}

\section*{Summary}
Motivated and technically skilled ex informatics student with a strong foundation in computer science principles and programming. 
Possesses fundamental knowledge in multiple programming languages including Python, Java, and C++. 
Experienced in system programming, algorithm design, and object-oriented programming. 
Proven ability to collaborate effectively on team projects and excel in problem-solving. 
\vspace{0.2in}

\section*{Skills}
\begin{tabbing}
    \hspace{1in} \= \hspace{1in} \= \hspace{1in} \= \hspace{1in} \= \kill
    \textbf{Computer Proficiency:} \= Python \textbullet \, Java \textbullet \, C++ \\
    \textbf{Leadership Experience:} \= Project management \textbullet \, Team leadership \textbullet \, Strategic planning \\
    \textbf{Communication Skills:} \= Public speaking \textbullet \, Technical writing \textbullet \, Negotiation \\
    \textbf{Organizational Know-how:} \= Time management \textbullet \, Task prioritization \textbullet \, Workflow optimization \\
    \textbf{People Skills:} \= Interpersonal communication \textbullet \, Conflict resolution \textbullet \, Empathy \\
    \textbf{Collaboration Talent:} \= Team collaboration \textbullet \, Cross-functional teamwork \textbullet \, Partnership development \\
    \textbf{Problem-solving Abilities:} \= Analytical thinking \textbullet \, Creative solutions \textbullet \, Decision making \\
\end{tabbing}

\begin{comment}
\vspace{0.2in}

\section*{Experience}
\begin{tabbing}
\hspace{3.5in} \= \hspace{2in} \= \kill
\textbf{Network Solutions LLC} \> Dallas, TX \> \textit{2019 - Ongoing} \\
\textbf{Lead Business Analyst \& Project Manager} \> \\
\end{tabbing}
\begin{itemize}[leftmargin=*]
    \item Created new strategies to manage \$2 million of accounts at risk, resulting in an increase of 4\% in revenue in 6 months.
    \item Led the effort to deploy an automated time \& expense reporting system for more than 90 onsite and offsite personnel across 3 locations.
    \item Oversaw the budget and schedule of a project to recruit, hire, and train 150 new employees at five new locations.
\end{itemize}

\begin{tabbing}
\hspace{3.5in} \= \hspace{2in} \= \kill
\textbf{Senior Business Analyst} \> \textit{2017 - 2019} \\
\end{tabbing}
\begin{itemize}[leftmargin=*]
    \item Through an improved pricing model, increased gross revenue of 15\% in 2018 compared to 2017 with no change to fixed costs.
    \item Reduced warehouse processing time by 30\% in just 3 months while industry norm is 10 months.
    \item Achieved project milestones and deliverables with an internal and external team of 10+ analysts.
\end{itemize}

\begin{tabbing}
\hspace{3.5in} \= \hspace{2in} \= \kill
\textbf{Lauzon} \> Dallas, TX \> \textit{2013 - 2016} \\
\textbf{Business Analyst} \> \\
\end{tabbing}
\begin{itemize}[leftmargin=*]
    \item Prepared 2016 Budget with Variance analysis to prior years.
    \item Assisted merger in advanced electronics space, identifying synergy opportunities of \$60M.
    \item Reduced IPS (Customer Issues) by 2.2\% while impacting merely 3\% of GMV.
    \item Designed and maintained 10+ data integration jobs.
\end{itemize}

\vspace{0.2in}
\end{comment}

\section*{Education}
\begin{tabbing}
\hspace{3.5in} \= \hspace{2in} \= \kill
\textbf{University of Lugano} \> Lugano \> \textit{2022 - 2024} \\
BInf: Programming, statistics \> \\
\\
\textbf{University of Zurich} \> Zurich \> \textit{2020 - 2021} \\
BEcon: Business, economics, finance \> \\\
\\
\textbf{SCC Bellinzona} \> Bellinzona \> \textit{2015 - 2019} \\
HSBD: Business, Accounting, law \> \\
\end{tabbing}

%\vspace{0.2in}

\section*{Certificates}
\begin{tabbing}
\hspace{3.5in} \= \hspace{2in} \= \kill
\textbf{Academic} \\
Commercial High School Diploma \> Bellinzona, 2019 \\
Federal Cantonal Certificate (AFC) \> Bellinzona, 2019 \\
\\
\textbf{Language} \\
English C2 \> Cambridge, 2022 \\
German C2 \> Munich, 2021 \\
\end{tabbing}

%\vspace{0.2in}

\section*{Interests \& Hobbies}
\begin{multicols}{3}
\justifying
\textbf{Programming} \\
Engage in personal projects
to enhance coding skills and
stay updated with new technologies.

\columnbreak

\justifying
\textbf{Chess} \\
Playing chess sharpens my 
problem-solving skills and 
strategic thinking.

\columnbreak

\justifying
\textbf{Team} \\
Participate in team activities 
to improve communication 
and teamwork abilities.
\end{multicols}





\end{document}
